MSDS6372Project1

### 2021-01-20 MSDS6372Project1.Rmd
fixing Engine.Fuel.Type and Mazda RX model missing values

**Data Import and Cleaning...**
```{r dataINC}
library(tidyverse)
# You need to adjust the work environment to run this code
setwd("/Users/mingyang/Desktop/SMU/Applied Statistics/MSDS6372Project1")
# Read in data under variable CarData
CarData = read.csv("data1.csv")
# In case there are NA character values
CarData[CarData=='NA'] <- NA
# Check the reading - can later be deleted
head(CarData)
str(CarData)
dim(CarData)
# Convert factor variables
variables.to.factor = c("Make","Model","Engine.Fuel.Type","Transmission.Type","Driven_Wheels","Market.Category","Vehicle.Size","Vehicle.Style")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)
# Look at summary of data
summary(CarData)
summary(CarData$Engine.Fuel.Type)

>>>>

**Data Import and Cleaning...**
```{r dataINC}
library(tidyverse)
# You need to adjust the work environment to run this code
setwd("/Users/mingyang/Desktop/SMU/Applied Statistics/MSDS6372Project1")
# Read in data under variable CarData
CarData = read.csv("data1.csv")
# Fixing three empty values in CarData$Engine.Fuel.Type, after research they are regular unleaded
CarData$Engine.Fuel.Type = ifelse(CarData$Engine.Fuel.Type=="","regular unleaded",CarData$Engine.Fuel.Type)
# Fixing Mazda RX model Engine Cylinders to 0
CarData$Engine.Cylinders = ifelse(CarData$Make=="Mazda"&is.na(CarData$Engine.Cylinders),0,CarData$Engine.Cylinders)
# Check the reading - can later be deleted
head(CarData)
str(CarData)
dim(CarData)
# Convert factor variables
variables.to.factor = c("Make","Model","Engine.Fuel.Type","Transmission.Type","Driven_Wheels","Market.Category","Vehicle.Size","Vehicle.Style")
CarData[variables.to.factor] = lapply(CarData[variables.to.factor],factor)
# Look at summary of data
summary(CarData)
summary(CarData$Market.Category)
